### 2016-09-06 Documents/bootcamp_project.tex
Update to project pdf.

One of our goals is for you to produce a piece of work you can use
to demonstrate your data and programming skills to potential employers.
That work will come in the form of an IPython/Jupyter notebook,
a format that combines code, text, and graphics in one user-friendly document.
We will add them to our GitHub repository so that
you can use a link to show others what you've done.
You will also be able to see what your classmates have done.

@@

The components of the project are
%
\begin{center}
\begin{tabular}{lllr}
\toprule
Assignment                  & Format  & Individual/Group &  Points \\
\midrule
Three Project Ideas         & Paper (hand-written)  & Individual  & 0  \\
Three Revised Project Ideas & Paper (professional)  & Individual  & 5  \\
Project Proposal            & Paper (professional)  & Group       & 5  \\
Data Report                 & Paper (professional)  & Group       & 5  \\
Final Project               & IPython/Jupyter notebook      & Group       & 85 \\
\bottomrule
\end{tabular}
\end{center}

@@

\item {\bf Final project.}
You should submit your {\bf IPython notebook\/} to \href{mailto:db3@nyu.edu}{db3@nyu.edu}
by the due date listed on the course website.
The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
depending on the section you are in.
The file name should be your last names separated by dashes and a short title ---
something like {\tt Jones-Smith-Zhang-India.ipynb}.

@@

Projects will be graded on their overall quality.  This includes, but is not restricted to,
these categories:
%
\begin{itemize}
\item Quality of the idea.  Is the question clearly articulated?  Is it interesting?
Does it have general appeal?
\item Quality of the data.  Does the data support the idea?
Is it the best data for this question?
\item Degree of difficulty.  Some ideas are harder than others to implement.
As in Olympic diving, you get credit for taking on a challenge.
\item Professional look.  Does your project look professional?  Are the graphs
easy to understand?  Are they clearly labeled?
\end{itemize}

>>>>

One of our goals is for you to produce a piece of work you can use
to demonstrate your data and programming skills to potential employers.
That work will come in the form of a Jupyter notebook,
a format that combines code, text, and graphics in one user-friendly document.
We will add them to our GitHub repository so that
you can use a link to show others what you've done.
You will also be able to see what your classmates have done.

@@

The components of the project are
%
\begin{center}
\begin{tabular}{lllr}
\toprule
Assignment                  & Format  & Individual/Group &  Points \\
\midrule
Three Project Ideas         & Paper (hand-written)  & Individual  & 0  \\
Three Revised Project Ideas & Paper (professional)  & Individual  & 5  \\
Project Proposal            & Paper (professional)  & Group       & 5  \\
Data Report                 & Paper (professional)  & Group       & 5  \\
Final Project               & Jupyter notebook      & Group       & 85 \\
\bottomrule
\end{tabular}
\end{center}

@@

\item {\bf Final project.}
You should submit your {\bf Jupyter notebook\/} to \href{mailto:nyu.databootcamp@gmail.com}{nyu.databootcamp@gmail.com}
by the due date listed on the course website.
The subject line should be:  ``bootcamp project ug'' or ``bootcamp project mba''
depending on the section you are in.
The file name should be your last names separated by dashes and a short title ---
something like {\tt Jones-Smith-Zhang-India.ipynb}.

@@

Projects will be graded on their overall quality.  This includes, but is not restricted to,
these categories:
%
\begin{itemize}
\item Quality of the idea.  Is the question clearly articulated?  Is it interesting?
Does it have general appeal?
\item Quality of the data.  Does the data support the idea?
Is it the best data for this question?
\item Quality of the code. Is the code readable? Could someone else understand what you were doing and why?
\item Degree of difficulty.  Some ideas are harder than others to implement.
As in Olympic diving, you get credit for taking on a challenge.
\item Professional look.  Does your project look professional?  Are the graphs
easy to understand?  Are they clearly labeled?
\end{itemize}
